Cybersecurity Is Too Important To Be Left To The Specialists

### 2019-01-28 ITiCSE2019.tex
Bug fixes
Added FIE abstract

\begin{abstract}
There are numerous facets to Cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). Whilst various model curricula and associated recommendations have been presented and discussed in recent years, in this paper we attempt to address the questions ``what should the generalist computer scientist know'' and ``how well is that being taught''.  (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters-level discipline or left to develop in professional practice, sometimes called ``information assurance'' in the UK and Europe, which worked, even if not well, in a waterfall model.

	In the world of software and systems development, we have seen the disruption of Agile (invented 2001) and DevOps (invented 2009), but not necessarily through the lens of security; however, more recently there has been a recognition of the need for change, exemplified by the emergence of ``DevSecOps''. If security is not to be left to the experts, then the generalist must know about it. Thus, in the context of widespread international computer science curriculum reform -- both in compulsory, as well as post-compulsory education -- what does this trend mean more generally for institutions and educators, and how do we teach it?

In this paper, we frame a key social and global challenge in computing education by analysing the UK perspective on Cybersecurity education, with a substantial national security, economic, and skills policy context, shaping the practical considerations for education professionals from schools through to universities. Through this analysis of policy and practice in the UK, we make a number of recommendations for future Cybersecurity educational initiatives, including practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions.
%292 words

% submitted abstract (hard 250 word limit):
% There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical; whilst various model curricula and associated recommendations have been presented and discussed in recent years, in this paper we attempt to address the questions ``what should the generalist computer scientist know'' and ``how well is that being taught''.  (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters-level discipline or left to develop in professional practice, sometimes called ``information assurance'' in the UK and Europe, which worked, even if not well, in a waterfall model. But if security is not to be left to the experts, then the generalist must know about it. Thus, in the context of widespread international computer science curriculum reform, what does this trend mean more generally for institutions and educators, and can do we teach it?

% In this paper, we frame a key social and global challenge in computing education by analysing the UK perspective on cybersecurity education, with a substantial national security, economic, and skills policy context, shaping the practical considerations for education professionals from schools through to universities. Through this analysis of policy and practice in the UK, we make a number of recommendations for future cybersecurity educational initiatives, including practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions.
\end{abstract}

>>>>

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). Whilst various national and international model curricula and recommendations have been presented and discussed in recent years, in this paper we attempt to address the questions ``what should the generalist computer scientist/engineer know'' and ``how well is that being taught''. (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters-level discipline; or left for development in professional practice, sometimes called “information assurance” in the UK and Europe, which worked, even if not well, in a sequential process model.

In the world of software and systems development, we have seen the disruption of Agile (invented c.2001) and DevOps (invented c.2009), but not necessarily through the lens of security; however, more recently there has been a recognition of the need for change, exemplified by the emergence of ``DevSecOps''. If security is not to be left to the experts, then the generalist must know about it. Thus, in the context of widespread international computer science/engineering curriculum reform – both in compulsory, as well as post-compulsory education – what does this trend mean more generally for institutions and educators, and how do we teach it?

In this paper, we frame a key social, cultural and economic global challenge in computing and engineering education by analysing the UK perspective on cybersecurity education, with a substantial national security, economic, and skills policy context, shaping the practical considerations for education professionals from schools through to universities. Through this analysis of policy and practice in the UK, we make a number of recommendations for future cybersecurity educational initiatives, including practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions. 
\end{abstract}
